Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-02-03 Manuscript/manuscript.tex
Added parts of text from NMRlipids4 paper for inspiration for writing.

@@

@@

>>>>

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
In the experimental $^2$H NMR literature data used in this work~\cite{browning80,roux90},
the lipids were first soluted to the buffer and then centrifuged to a pellet which
was used in the measurements. Such samples have lower lipid concentration
(approximately 10~wt~\% of lipids~\cite{browning80,roux88,roux90}) than 
gravimetric samples (60~wt~\%) and simulations (approximately 50-60~wt~\%) in this work.
Larger multilamellar repeat distances are expected in the samples with lower lipid
concentrations due to the swelling caused by electrostatic repulsion in pure PS lipid systems~\cite{millman82}.
However, the PS headgroup order parameters measured from gravimetric sample in this work
are in good agreement with the results from centrifuged sample in the literature \cite{browning80} (Fig. \ref{HGorderParameters}).
Furthermore, the equlibrium repeat distance rapidly decreases with the addtion of monovalent
salts and is close to the simulation box sizes already above 500~mM concentrations~\cite{millman82,rand89}.
Therefore, the hydration levels of multilamellae are expected to be sufficiently similar
in the used simulations and reference experiments.

@@

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
The headgroup order parameters
of negatively charged PS and PG lipids exhibit systemic, but less
characterized dependence on the bound charge~\cite{borle85,macdonald87,roux86,roux90}.
Therefore, the ion binding affinity to negatively charged bilayers
can be better characterized by measuring the PC headgroup order parameters from 
mixed bilayers~\cite{roux86,roux90,roux91},

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
Previous experimental studies have concluded that
PS headgroups are more rigid than phophocholines (PC)
due to the hydrogen bonding network or
electrostatic interactions \cite{browning80,buldt81}.
%
Dilution of bilayers with PC lipids makes PS headgroups
less rigid and reduces propensity for the formation of
strong complexes with multivalent ions \cite{browning80,buldt81,roux90,roux91}.
The molecular level interpretation of these observations is,
however, not available.

@@

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
The dehydrated complexes of PS headgroup and calcium ions can also lead to the
phase separation \cite{hauser77,kurland79,hauser85,feigenson86,mattai89,roux90,roux91}.
%
CHARMM36 force field \cite{klauda10,venable13} combined with 2D infrared spectroscopy
suggests that calcium ions interacts only with the carboxylate group of PS lipids \cite{valentine18}, while
the same force field without the NBfix parameters together with the NMR chemical shifts and
REDOR experiments suggests a significant binding affinity also to the phosphate region \cite{hallock18}.
On the other hand, simulations with the Berger force field \cite{berger97,mukhopadhyay04}
combined with fluorescent and vibrational sum frequency spectroscopy suggested a significant
calcium binding also to the carbonyls in the acyl chains \cite{melcrova16}.
